Titeln på avhandlingens språk

### 2022-08-30 model.tex
plotting

We begin by discretizing neuroticism and \ac{TTF} each into terciles; we will refer to the first, second, and third terciles of neuroticism as \emph{low}, \emph{medium}, and \emph{high} neuroticism respectively, and to the corresponding terciles of \ac{TTF} as \emph{low}, \emph{medium}, and \emph{high impairment}.

@@

The results of this processing on the samples from \cref{tab:data:exectime} can be seen in \cref{tab:data:exectime:processed}

\begin{table*}
\caption{Sample of the processed execution time data table.}\label{tab:data:exectime:processed}
\begin{tabular}{rrrrcrccrc}
\toprule
{seq} & {run\_id} & {next\_exec\_time} & {ttf} & {impairment} & {neuroticism\_raw} & {neuroticism} & {transition} & {duration\_raw} & {duration} \\
\midrule
1   & 134146 & 3.655 & 0.000 & low & 0.375  & low& NoTransition & 1 & short \\
2   & 134146 & 4.439 & 0.597 & low & 0.375 & low & NoTransition & 2 & short \\
3   & 134146 & 2.943 & 0.554 & low & 0.375 & low & NoTransition & 3 & short \\
\( \cdots \) & \( \cdots \) & \( \cdots \) & \( \cdots \) & \( \cdots \) & \( \cdots \) & \( \cdots \) & \( \cdots \) & \( \cdots \) & \( \cdots \)\\
169 & 134146 & 3.532 & 3.689 & high & 0.375 & low & Lower2Higher & 2 & short \\
1   & 134470 & 3.461 & 0.000 & low & 0.594 & med & NoTransition & 1 & short \\
2   & 134470 & 6.678 & 0.561 & low & 0.594 & med & NoTransition & 2 & short \\
\( \cdots \) & \( \cdots \) & \( \cdots \) & \( \cdots \) & \( \cdots \) & \( \cdots \) & \( \cdots \) & \( \cdots \) & \( \cdots \) & \( \cdots \)\\
\( \cdots \) & \( \cdots \) & \( \cdots \) & \( \cdots \) & \( \cdots \) & \( \cdots \) & \( \cdots \) & \( \cdots \) & \( \cdots \) & \( \cdots \)\\
169 & 137353 & 4.615 & 0.579 & low & 0.625 & med & NoTransition & 2 & short \\
\bottomrule
\end{tabular}
\end{table*}

\begin{figure*}
    \centering
    \begin{subfigure}[t]{\columnwidth}
        \centering
        \includegraphics[width=.8\columnwidth]{./model_data/duration_vs_exectime.png}
        \caption{}\label{fig:timing:durvsetime}
    \end{subfigure}%
    \begin{subfigure}[t]{\columnwidth}
        \centering
        \includegraphics[width=.8\columnwidth]{./model_data/impairment_transition_vs_exectime.png}
        \caption{}\label{fig:timing:imptransvsetime}
    \end{subfigure}
    \caption{\cref{fig:timing:durvsetime} shows how the model captures the speed-up and slow-down behaviors due to impairment and duration described in \textcite{olguinmunoz:impact2021}}
\end{figure*}

>>>>

We begin by discretizing normalized neuroticism into \emph{low} and \emph{high} ranges, \( [0.0, 0.5) \) and \( [0.5, 1.0) \) respectively. 
We also bin \ac{TTF} into terciles; we will refer to the first, second, and third terciles of \ac{TTF} as \emph{low}, \emph{medium}, and \emph{high impairment}.

@@

The results of this processing on the samples from \cref{tab:data:exectime} can be seen in \cref{tab:data:exectime:processed}.
Three examples of the effect of this discretization and processing on the data are also presented in \cref{fig:timing}.

\begin{table*}
\caption{Sample of the processed execution time data table.}\label{tab:data:exectime:processed}
\begin{tabular}{rrrrcrccrc}
\toprule
{seq} & {run\_id} & {next\_exec\_time} & {ttf} & {impairment} & {neuroticism\_raw} & {neuroticism} & {transition} & {duration\_raw} & {duration} \\
\midrule
1   & 134146 & 3.655 & 0.000 & low & 0.375  & low & NoTransition & 1 & short \\
2   & 134146 & 4.439 & 0.597 & low & 0.375 & low & NoTransition & 2 & short \\
3   & 134146 & 2.943 & 0.554 & low & 0.375 & low & NoTransition & 3 & short \\
\( \cdots \) & \( \cdots \) & \( \cdots \) & \( \cdots \) & \( \cdots \) & \( \cdots \) & \( \cdots \) & \( \cdots \) & \( \cdots \) & \( \cdots \)\\
169 & 134146 & 3.532 & 3.689 & high & 0.375 & low & Lower2Higher & 2 & short \\
1   & 134470 & 3.461 & 0.000 & low & 0.594 & high & NoTransition & 1 & short \\
2   & 134470 & 6.678 & 0.561 & low & 0.594 & high & NoTransition & 2 & short \\
\( \cdots \) & \( \cdots \) & \( \cdots \) & \( \cdots \) & \( \cdots \) & \( \cdots \) & \( \cdots \) & \( \cdots \) & \( \cdots \) & \( \cdots \)\\
\( \cdots \) & \( \cdots \) & \( \cdots \) & \( \cdots \) & \( \cdots \) & \( \cdots \) & \( \cdots \) & \( \cdots \) & \( \cdots \) & \( \cdots \)\\
169 & 137353 & 4.615 & 0.579 & low & 0.625 & high & NoTransition & 2 & short \\
\bottomrule
\end{tabular}
\end{table*}

\begin{figure*}
    \centering
    \begin{subfigure}[t]{\columnwidth}
        \centering
        \includegraphics[width=.8\columnwidth]{./model_data/imp_neur_vs_exectime.png}
        \caption{}\label{fig:timing:impneurvsetime}
    \end{subfigure}\\
    \begin{subfigure}[t]{\columnwidth}
        \centering
        \includegraphics[width=.8\columnwidth]{./model_data/duration_vs_exectime.png}
        \caption{}\label{fig:timing:durvsetime}
    \end{subfigure}%
    \begin{subfigure}[t]{\columnwidth}
        \centering
        \includegraphics[width=.8\columnwidth]{./model_data/impairment_transition_vs_exectime.png}
        \caption{}\label{fig:timing:imptransvsetime}
    \end{subfigure}
    \caption{%
        Visualizations of the model data after discretization and post-processing.
        \subref{fig:timing:impneurvsetime} illustrates the effect of impairment on execution times, and how neuroticism modulates this behavior;
        \subref{fig:timing:durvsetime} exemplifies how the model captures the speed-up and slow-down behaviors due to impairment and duration described in \textcite{olguinmunoz:impact2021};
        finally, \subref{fig:timing:imptransvsetime} shows the lingering effects of impairment after a transition.
    }\label{fig:timing}
\end{figure*}
